Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/hybrid_zone.tex
reset changes that were breaking supplement

Power will be optimal at intermediate values of $s$.
If selection is too strong, it may be difficult to observe this signal
due to a lack of introgressed selected sites,
while if selection is weak, the selected lineage does not move very fast,
and so the strength of signal from elevated $l_B(m)$ is diminished \alisa{(Fig.~\ref{sfig:blockLengthPlot_t1000_s0.001})}. 
Indeed, if $s$ is less than $x/(\sigma T)$, then only one block of ancestry $A$ is expected to be seen about a selected $A$ allele,
and $l_A(x,m)$ is expected to be $2/T$.
For similar reasons, power and resolution are best at intermediate $T$.

>>>>

Power will be optimal at intermediate values of $s$.
If selection is too strong, it may be difficult to observe this signal
due to a lack of introgressed selected sites,
while if selection is weak, the selected lineage does not move very fast,
and the hybrid zone is wider, allowing more recombination,
and so the strength of signal from elevated $l_B(m)$ is diminished.
For instance, no signal is seen in Figure~\ref{sfig:blockLengthPlot_t1000_s0.001}.
% Indeed, if $s$ is less than $x/(\sigma T)$, then only one block of ancestry $A$ is expected to be seen about a selected $A$ allele,
% and $l_A(x,m)$ is expected to be $2/T$.
For similar reasons, power and resolution are best at intermediate $T$.
